---
title: "Exploring History"
output: 
  html_document:
    toc: false
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->
#### [Back to Main Menu](git_intro.html)   
#### [Back](git_3.html) [Next](git_5.html)   

```{r setup, echo=FALSE}
knitr::opts_knit$set(root.dir = '~/Desktop/planets')
```

If we want to see what we changed at different steps, we can use `git diff`
again, but with the notation `HEAD~1`, `HEAD~2`, and so on, to refer to old
commits:

```{bash}
git diff HEAD~1 mars.txt
```

In this way,
we can build up a chain of commits.
The most recent end of the chain is referred to as `HEAD`;
we can refer to previous commits using the `~` notation,
so `HEAD~1` (pronounced "head minus one")
means "the previous commit",
while `HEAD~123` goes back 123 commits from where we are now.


We can also refer to commits using
those long strings of digits and letters
that `git log` displays.
These are unique IDs for the changes,
and "unique" really does mean unique:
every change to any set of files on any computer
has a unique 40-character identifier.
Our first commit was given the ID
f22b25e3233b4645dabd0d81e651fe074bd8e73b,
so let's try this:

```{bash, eval=FALSE}
git diff f22b25e3233b4645dabd0d81e651fe074bd8e73b mars.txt

```
```{bash, echo=FALSE}
git diff HEAD~1 mars.txt
```

That's the right answer,
but typing out random 40-character strings is annoying,
so Git lets us use just the first few characters:

```{bash, eval=FALSE}
git diff f22b25e mars.txt
```

```{bash, echo=FALSE}
git diff HEAD~1 mars.txt
```

All right! So
we can save changes to files and see what we've changed&mdash;now how
can we restore older versions of things?
Let's suppose we accidentally overwrite our file:

```{bash, eval=FALSE}
nano mars.txt
```

```{bash, echo=FALSE}
echo "We will need to manufacture our own oxygen" > mars.txt
cat mars.txt
```

We can put things back the way they were
by using `git checkout`:

```{bash}
git checkout HEAD mars.txt
cat mars.txt
```

As you might guess from its name,
`git checkout` checks out (i.e., restores) an old version of a file.
In this case,
we're telling Git that we want to recover the version of the file recorded in `HEAD`,
which is the last saved commit.
If we want to go back even further,
we can use a commit identifier instead:

```{bash, eval=FALSE}
git checkout f22b25e mars.txt
```

It's important to remember that
we must use the commit number that identifies the state of the repository
*before* the change we're trying to undo.
A common mistake is to use the number of
the commit in which we made the change we're trying to get rid of.
In the example below, we want to retrieve the state from before the most
recent commit (`HEAD~1`), which is commit `f22b25e`:

#### [Next](git_5.html)   

<!-- Insert the session information into the document -->
