---
title: "GitHub"
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->
## Remote repositories are and why they are useful.
> *   Clone a remote repository. 
> *   Push to or pull from a remote repository.

Version control really comes into its own
when we begin to collaborate with other people.
We already have most of the machinery we need to do this;
the only thing missing is to copy changes from one repository to another.

Systems like Git allow us to move work between any two repositories.
In practice,
though,
it's easiest to use one copy as a central hub,
and to keep it on the web rather than on someone's laptop.
Most programmers use hosting services like
[GitHub](http://github.com),
[BitBucket](http://bitbucket.org) or
[GitLab](http://gitlab.com/)
to hold those master copies;
we'll explore the pros and cons of this in the final section of this lesson.

Let's start by sharing the changes we've made to our current project with the world.
Log in to GitHub,
then click on the icon in the top right corner to create a new repository called `planets`.  

Name your repository "planets" and then click "Create Repository".  "
As soon as the repository is created,
GitHub displays a page with a URL and some information on how to configure your local repository.  

This effectively does the following on GitHub's servers:

```{bash, eval=FALSE}
mkdir planets
cd planets
git init
```

Our local repository still contains our earlier work on `mars.txt`,
but the remote repository on GitHub doesn't contain any files yet:

The next step is to connect the two repositories.
We do this by making the GitHub repository a [remote](reference.html#remote)
for the local repository.
The home page of the repository on GitHub includes
the string we need to identify it.  

Copy that URL from the browser,
go into the local `planets` repository,
and run this command:

```{bash, eval=FALSE}
git remote add origin https://github.com/vlad/planets
```

```{bash, echo=FALSE, eval=FALSE}
git remote add origin https://github.com/smozaffari/planets
```

Make sure to use the URL for your repository rather than Vlad's:
the only difference should be your username instead of `vlad`.

We can check that the command has worked by running `git remote -v`

```{bash, eval=FALSE}
git remote -v
```

```{output}
origin   https://github.com/vlad/planets.git (push)
origin   https://github.com/vlad/planets.git (fetch)
```
