---
title: "Resources"
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis', include=FALSE}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis', include=FALSE}
```

<!-- Add your analysis here -->

Some additional resources to practice your new skills and to learn more:  

* To get your free private repos for students on github go [here](https://education.github.com/pack)  

* Practicing using git and github by going through [John Blischak's paper](http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1004668).  

* Check out [Software Carpentry](https://software-carpentry.org/lessons/) for more resources on using Unix, git, R, python, and SQL.  

* To learn more of Unix, git, R, python, LaTeX, SQL, and more, consider sitting in on (or taking!) [Stefano Allesina's course Intro Sci Comp](http://allesinalab.uchicago.edu/?page_id=35). You can also look at the [notes published from 2014](http://allesinalab.uchicago.edu/wp-content/uploads/2014/05/IntroSciComp2014.pdf).

* Sign up for future seminars and take a look at previous computational workshops put on by the CRI [here](https://cri.uchicago.edu/seminar-series/).

* To integrate R with git and make a nice website like this one really easily, check out [workflowr](https://jdblischak.github.io/workflowr/) R package by John Blischak.  


Depending what you want to do there are always more resources we can point you to!


