---
title: "Intro to using the Terminal"
author: "Sahar Mozaffari"
date: 2017-07-28
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

*  *  *  *
##Getting Started

###For OSx:

Open ```/Applications/Utilities/Terminal```
  Keep in Dock for easy access.

###For Unix:

Search applications for Terminal  
Keep in Launcher, if you have one, for easy access

###For Windows:

Download Console 2  
Extract Console.exe  
Add Console.exe shortcut to Desktop  
Open Console.exe, go to Edit->Settings and set the shell to PowerShell ```(C:\WINDOWS\system32\WindowsPowerShell\v1.0\powershell.exe)```  
Set the Startup dir to your User directory  
Restart Console.exe  

*  *  *  *
##Getting Help
Here are some commands you can type once you have a terminal open:

####Manual

```man <command>```: Opens manual page for command. Move up/down with arrow keys, press q to quit

####Listing with details  
```ls```: List all non-hidden files/folders  
```ls -a```: List all files/folders  
```ls -l```: Details list of available files/folders


*  *  *  *
##Moving Around  

####Current path  
```pwd```: lists current path (present working directory)  

####Change directory  
```cd <directory>```: Changes directory to entered directory (case sensitive)  
          Folders with spaces in name need to escape space: foo\\ bar  

####Current directory
```.```: Starts at the current directory  

####Moving backward
```..``` : Steps back a directory 
ex. ```cd ..``: changes directory to the directory above   
ex. ```ls .```: lists all non-hidden files in directory above   
 

####User directory
```~```: Start at your user directory  

*  *  *  *
*  *  *  *
##Files and Folders

####Creating folders
```mkdir <foldername> ``` : Makes a folder  

####Removing empty folders
```rmdir <foldername>``` : Removes an empty folder  

####Creating files
```emacs <file-name>``` 

####Reading and Writing to files
```echo <content>``` : Will write content to a file  
```cat <filename>``` : Will preview all content in a file  

####Moving and renaming Files
```mv <filename> <newfilename>``` : Will move or rename file  

####Removing files
`r emo::ji("alert")` `r emo::ji("alert")` `r emo::ji("alert")`  
```rm <filename>``` : Deletes file (DOES NOT MOVE TO TRASH! CANNOT UNDO!)  `r emo::ji("alert")`

<!-- Insert the session information into the document -->
```{r session-info, eval=FALSE, echo = FALSE}
## Session information

```
